Online Appendix for \\ Enemy at the Gates: Variation in Economic Growth from Civil Conflict

### 2016-01-23 LaTeX/TeX/Manuscript/Graphics/mCapSimPlot.tex
reorg for final submission to jcr

% Created by tikzDevice version 0.7.0 on 2014-10-06 20:10:12
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 35.42, 34.03) rectangle (421.57,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,105.17) --
	( 60.61,107.79) --
	( 64.85,109.25) --
	( 64.98,109.30) --
	( 78.30,113.88) --
	( 86.71,116.78) --
	( 92.34,118.71) --
	( 95.59,119.83) --
	(101.92,122.01) --
	(110.88,125.09) --
	(154.64,140.15) --
	(158.01,141.31) --
	(171.43,145.93) --
	(178.49,148.35) --
	(187.92,151.60) --
	(192.71,153.25) --
	(195.62,154.25) --
	(195.71,154.28) --
	(196.35,154.50) --
	(198.04,155.08) --
	(199.87,155.71) --
	(204.99,157.47) --
	(205.19,157.54) --
	(209.65,159.08) --
	(211.50,159.71) --
	(215.87,161.22) --
	(217.33,161.72) --
	(217.43,161.75) --
	(217.68,161.84) --
	(218.17,162.01) --
	(220.17,162.70) --
	(220.33,162.75) --
	(220.93,162.96) --
	(221.63,163.20) --
	(222.58,163.53) --
	(223.29,163.77) --
	(223.54,163.86) --
	(223.59,163.87) --
	(224.00,164.02) --
	(229.14,165.78) --
	(231.15,166.48) --
	(231.34,166.54) --
	(232.39,166.90) --
	(233.34,167.23) --
	(234.24,167.54) --
	(235.24,167.88) --
	(236.22,168.22) --
	(237.40,168.63) --
	(237.41,168.63) --
	(239.29,169.28) --
	(239.31,169.28) --
	(240.03,169.53) --
	(240.80,169.79) --
	(241.27,169.96) --
	(241.65,170.09) --
	(242.95,170.54) --
	(244.78,171.17) --
	(248.30,172.38) --
	(249.74,172.87) --
	(250.22,173.04) --
	(250.38,173.09) --
	(250.69,173.20) --
	(251.97,173.64) --
	(252.46,173.81) --
	(253.69,174.23) --
	(253.89,174.30) --
	(254.34,174.45) --
	(255.73,174.94) --
	(256.94,175.35) --
	(258.99,176.06) --
	(260.08,176.43) --
	(260.16,176.46) --
	(261.39,176.88) --
	(262.57,177.29) --
	(263.47,177.60) --
	(264.14,177.83) --
	(264.43,177.93) --
	(264.94,178.10) --
	(265.11,178.16) --
	(265.48,178.29) --
	(265.54,178.31) --
	(266.69,178.71) --
	(266.70,178.71) --
	(267.74,179.07) --
	(267.83,179.10) --
	(267.95,179.14) --
	(268.15,179.21) --
	(268.32,179.26) --
	(268.51,179.33) --
	(268.75,179.41) --
	(269.12,179.54) --
	(269.30,179.60) --
	(269.75,179.76) --
	(269.91,179.81) --
	(271.51,180.36) --
	(272.31,180.64) --
	(272.40,180.67) --
	(272.91,180.84) --
	(273.01,180.88) --
	(273.29,180.98) --
	(273.48,181.04) --
	(274.31,181.33) --
	(274.85,181.51) --
	(274.88,181.52) --
	(275.50,181.74) --
	(276.03,181.92) --
	(276.14,181.95) --
	(276.73,182.16) --
	(276.77,182.17) --
	(277.28,182.35) --
	(277.37,182.38) --
	(278.83,182.88) --
	(278.93,182.92) --
	(278.99,182.94) --
	(279.03,182.95) --
	(279.36,183.06) --
	(279.83,183.23) --
	(279.90,183.25) --
	(280.21,183.36) --
	(280.36,183.41) --
	(280.41,183.43) --
	(280.47,183.45) --
	(280.50,183.46) --
	(280.60,183.49) --
	(280.63,183.50) --
	(281.16,183.68) --
	(281.52,183.81) --
	(281.60,183.84) --
	(283.10,184.35) --
	(283.28,184.41) --
	(283.34,184.44) --
	(283.74,184.57) --
	(283.80,184.59) --
	(284.26,184.75) --
	(284.43,184.81) --
	(284.75,184.92) --
	(284.80,184.94) --
	(284.81,184.94) --
	(284.81,184.94) --
	(284.84,184.95) --
	(284.88,184.96) --
	(285.44,185.16) --
	(285.67,185.24) --
	(286.04,185.36) --
	(286.70,185.59) --
	(286.95,185.68) --
	(287.76,185.96) --
	(288.16,186.09) --
	(288.45,186.19) --
	(288.86,186.33) --
	(289.03,186.39) --
	(289.13,186.43) --
	(289.30,186.48) --
	(289.61,186.59) --
	(289.71,186.63) --
	(289.99,186.72) --
	(290.44,186.88) --
	(291.29,187.17) --
	(291.45,187.22) --
	(291.58,187.27) --
	(292.20,187.48) --
	(292.36,187.54) --
	(292.77,187.68) --
	(292.78,187.68) --
	(292.85,187.71) --
	(292.94,187.74) --
	(293.49,187.93) --
	(293.61,187.97) --
	(293.90,188.07) --
	(293.94,188.08) --
	(295.12,188.49) --
	(295.85,188.74) --
	(296.61,189.00) --
	(297.11,189.17) --
	(297.99,189.47) --
	(298.09,189.51) --
	(298.13,189.52) --
	(298.21,189.55) --
	(298.45,189.63) --
	(298.48,189.64) --
	(298.71,189.72) --
	(298.89,189.79) --
	(299.22,189.90) --
	(300.07,190.19) --
	(300.69,190.40) --
	(301.34,190.63) --
	(301.81,190.79) --
	(301.86,190.81) --
	(302.06,190.87) --
	(302.08,190.88) --
	(302.20,190.93) --
	(302.30,190.96) --
	(302.45,191.01) --
	(302.52,191.03) --
	(302.61,191.06) --
	(302.89,191.16) --
	(302.93,191.17) --
	(303.17,191.26) --
	(304.10,191.58) --
	(304.31,191.65) --
	(304.47,191.71) --
	(304.48,191.71) --
	(304.60,191.75) --
	(304.68,191.78) --
	(305.11,191.93) --
	(305.28,191.98) --
	(305.76,192.15) --
	(305.86,192.18) --
	(306.15,192.28) --
	(307.03,192.59) --
	(307.16,192.63) --
	(307.37,192.70) --
	(308.42,193.06) --
	(308.63,193.14) --
	(308.79,193.19) --
	(309.08,193.29) --
	(309.55,193.45) --
	(309.72,193.51) --
	(310.36,193.73) --
	(310.45,193.76) --
	(310.80,193.88) --
	(310.98,193.95) --
	(311.09,193.98) --
	(311.49,194.12) --
	(311.71,194.20) --
	(311.87,194.25) --
	(312.39,194.43) --
	(312.68,194.53) --
	(312.75,194.55) --
	(314.09,195.02) --
	(314.12,195.02) --
	(314.55,195.17) --
	(314.84,195.27) --
	(315.05,195.34) --
	(315.28,195.42) --
	(315.54,195.51) --
	(315.61,195.54) --
	(315.65,195.55) --
	(316.29,195.77) --
	(316.37,195.80) --
	(316.58,195.87) --
	(316.61,195.88) --
	(316.72,195.92) --
	(317.13,196.06) --
	(318.60,196.57) --
	(319.14,196.75) --
	(320.71,197.29) --
	(321.34,197.51) --
	(321.47,197.55) --
	(322.56,197.93) --
	(322.64,197.96) --
	(322.93,198.06) --
	(323.98,198.42) --
	(324.06,198.44) --
	(324.53,198.61) --
	(324.82,198.71) --
	(325.46,198.93) --
	(325.85,199.06) --
	(325.87,199.07) --
	(325.91,199.08) --
	(326.16,199.17) --
	(326.46,199.27) --
	(327.01,199.46) --
	(327.50,199.63) --
	(327.78,199.72) --
	(328.37,199.93) --
	(328.92,200.12) --
	(330.17,200.55) --
	(330.38,200.62) --
	(330.88,200.79) --
	(333.53,201.71) --
	(333.56,201.71) --
	(333.69,201.76) --
	(333.82,201.80) --
	(333.83,201.81) --
	(335.38,202.34) --
	(335.47,202.37) --
	(337.65,203.12) --
	(338.50,203.41) --
	(338.83,203.53) --
	(338.87,203.54) --
	(339.04,203.60) --
	(339.21,203.66) --
	(339.40,203.72) --
	(339.55,203.77) --
	(339.76,203.85) --
	(339.84,203.88) --
	(340.15,203.98) --
	(340.28,204.03) --
	(340.65,204.15) --
	(341.52,204.45) --
	(342.53,204.80) --
	(343.79,205.23) --
	(343.95,205.29) --
	(345.11,205.69) --
	(345.20,205.72) --
	(345.78,205.92) --
	(346.49,206.16) --
	(346.80,206.27) --
	(346.94,206.32) --
	(347.30,206.44) --
	(348.63,206.90) --
	(348.84,206.97) --
	(349.59,207.23) --
	(350.01,207.38) --
	(350.27,207.46) --
	(350.57,207.57) --
	(351.61,207.93) --
	(352.50,208.23) --
	(354.60,208.95) --
	(354.77,209.01) --
	(355.03,209.10) --
	(355.06,209.11) --
	(355.38,209.22) --
	(355.44,209.24) --
	(355.66,209.32) --
	(355.69,209.33) --
	(356.06,209.46) --
	(356.08,209.46) --
	(356.57,209.63) --
	(356.86,209.73) --
	(356.99,209.78) --
	(357.04,209.79) --
	(357.10,209.81) --
	(357.28,209.88) --
	(357.68,210.01) --
	(357.71,210.02) --
	(358.36,210.25) --
	(358.45,210.28) --
	(358.80,210.40) --
	(359.58,210.67) --
	(360.14,210.86) --
	(360.17,210.87) --
	(360.28,210.91) --
	(360.68,211.05) --
	(362.54,211.69) --
	(362.92,211.82) --
	(362.99,211.84) --
	(362.99,211.84) --
	(363.68,212.08) --
	(363.71,212.09) --
	(364.25,212.28) --
	(364.57,212.39) --
	(364.77,212.45) --
	(365.00,212.53) --
	(365.26,212.62) --
	(365.84,212.82) --
	(365.84,212.82) --
	(365.92,212.85) --
	(366.04,212.89) --
	(366.47,213.04) --
	(367.05,213.24) --
	(368.20,213.63) --
	(368.39,213.70) --
	(368.50,213.74) --
	(370.21,214.32) --
	(371.17,214.65) --
	(371.58,214.80) --
	(372.02,214.95) --
	(373.58,215.48) --
	(376.96,216.65) --
	(378.52,217.19) --
	(383.85,219.02) --
	(384.44,219.22) --
	(384.92,219.39) --
	(385.30,219.52) --
	(385.73,219.66) --
	(385.96,219.74) --
	(386.70,220.00) --
	(386.81,220.04) --
	(387.17,220.16) --
	(387.19,220.17) --
	(387.24,220.18) --
	(387.39,220.24) --
	(387.67,220.34) --
	(388.26,220.54) --
	(389.16,220.85) --
	(389.82,221.07) --
	(390.40,221.27) --
	(390.44,221.29) --
	(390.79,221.41) --
	(391.07,221.50) --
	(395.16,222.91) --
	(396.00,223.20) --
	(396.15,223.25) --
	(403.52,225.79) --
	(404.02,225.96);

@@

\path[fill=fillColor,fill opacity=0.30] ( 52.97,165.07) --
	( 60.61,166.03) --
	( 64.85,166.51) --
	( 64.98,166.54) --
	( 78.30,168.33) --
	( 86.71,169.61) --
	( 92.34,170.44) --
	( 95.59,171.03) --
	(101.92,171.81) --
	(110.88,172.89) --
	(154.64,180.05) --
	(158.01,180.45) --
	(171.43,182.73) --
	(178.49,184.08) --
	(187.92,185.93) --
	(192.71,186.77) --
	(195.62,187.27) --
	(195.71,187.28) --
	(196.35,187.38) --
	(198.04,187.65) --
	(199.87,188.05) --
	(204.99,189.01) --
	(205.19,189.03) --
	(209.65,190.06) --
	(211.50,190.52) --
	(215.87,191.59) --
	(217.33,191.90) --
	(217.43,191.93) --
	(217.68,191.97) --
	(218.17,192.07) --
	(220.17,192.44) --
	(220.33,192.49) --
	(220.93,192.59) --
	(221.63,192.75) --
	(222.58,192.98) --
	(223.29,193.13) --
	(223.54,193.18) --
	(223.59,193.19) --
	(224.00,193.30) --
	(229.14,194.56) --
	(231.15,194.97) --
	(231.34,194.99) --
	(232.39,195.37) --
	(233.34,195.60) --
	(234.24,195.69) --
	(235.24,195.85) --
	(236.22,196.18) --
	(237.40,196.49) --
	(237.41,196.49) --
	(239.29,197.05) --
	(239.31,197.06) --
	(240.03,197.23) --
	(240.80,197.39) --
	(241.27,197.46) --
	(241.65,197.55) --
	(242.95,197.83) --
	(244.78,198.38) --
	(248.30,199.35) --
	(249.74,199.77) --
	(250.22,199.91) --
	(250.38,199.94) --
	(250.69,200.06) --
	(251.97,200.42) --
	(252.46,200.53) --
	(253.69,200.79) --
	(253.89,200.86) --
	(254.34,200.96) --
	(255.73,201.43) --
	(256.94,201.82) --
	(258.99,202.54) --
	(260.08,202.88) --
	(260.16,202.90) --
	(261.39,203.25) --
	(262.57,203.64) --
	(263.47,203.91) --
	(264.14,204.11) --
	(264.43,204.22) --
	(264.94,204.38) --
	(265.11,204.45) --
	(265.48,204.57) --
	(265.54,204.59) --
	(266.69,205.01) --
	(266.70,205.01) --
	(267.74,205.35) --
	(267.83,205.37) --
	(267.95,205.45) --
	(268.15,205.52) --
	(268.32,205.56) --
	(268.51,205.63) --
	(268.75,205.74) --
	(269.12,205.89) --
	(269.30,205.97) --
	(269.75,206.12) --
	(269.91,206.17) --
	(271.51,206.69) --
	(272.31,207.01) --
	(272.40,207.06) --
	(272.91,207.29) --
	(273.01,207.33) --
	(273.29,207.43) --
	(273.48,207.49) --
	(274.31,207.72) --
	(274.85,207.89) --
	(274.88,207.90) --
	(275.50,208.11) --
	(276.03,208.30) --
	(276.14,208.34) --
	(276.73,208.55) --
	(276.77,208.57) --
	(277.28,208.75) --
	(277.37,208.78) --
	(278.83,209.26) --
	(278.93,209.30) --
	(278.99,209.33) --
	(279.03,209.34) --
	(279.36,209.43) --
	(279.83,209.54) --
	(279.90,209.57) --
	(280.21,209.70) --
	(280.36,209.75) --
	(280.41,209.78) --
	(280.47,209.80) --
	(280.50,209.81) --
	(280.60,209.85) --
	(280.63,209.85) --
	(281.16,210.05) --
	(281.52,210.20) --
	(281.60,210.24) --
	(283.10,210.77) --
	(283.28,210.82) --
	(283.34,210.83) --
	(283.74,210.94) --
	(283.80,210.97) --
	(284.26,211.19) --
	(284.43,211.24) --
	(284.75,211.33) --
	(284.80,211.34) --
	(284.81,211.34) --
	(284.81,211.34) --
	(284.84,211.35) --
	(284.88,211.37) --
	(285.44,211.54) --
	(285.67,211.63) --
	(286.04,211.78) --
	(286.70,212.02) --
	(286.95,212.12) --
	(287.76,212.51) --
	(288.16,212.63) --
	(288.45,212.70) --
	(288.86,212.81) --
	(289.03,212.87) --
	(289.13,212.93) --
	(289.30,212.99) --
	(289.61,213.12) --
	(289.71,213.16) --
	(289.99,213.26) --
	(290.44,213.43) --
	(291.29,213.72) --
	(291.45,213.79) --
	(291.58,213.85) --
	(292.20,214.08) --
	(292.36,214.13) --
	(292.77,214.30) --
	(292.78,214.30) --
	(292.85,214.32) --
	(292.94,214.36) --
	(293.49,214.59) --
	(293.61,214.64) --
	(293.90,214.77) --
	(293.94,214.79) --
	(295.12,215.21) --
	(295.85,215.51) --
	(296.61,215.83) --
	(297.11,216.04) --
	(297.99,216.40) --
	(298.09,216.45) --
	(298.13,216.47) --
	(298.21,216.50) --
	(298.45,216.60) --
	(298.48,216.61) --
	(298.71,216.72) --
	(298.89,216.80) --
	(299.22,216.90) --
	(300.07,217.25) --
	(300.69,217.51) --
	(301.34,217.77) --
	(301.81,217.95) --
	(301.86,217.97) --
	(302.06,218.06) --
	(302.08,218.06) --
	(302.20,218.12) --
	(302.30,218.16) --
	(302.45,218.22) --
	(302.52,218.25) --
	(302.61,218.29) --
	(302.89,218.40) --
	(302.93,218.42) --
	(303.17,218.52) --
	(304.10,218.84) --

>>>>

% Created by tikzDevice version 0.7.0 on 2014-10-09 04:51:37
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 35.42, 34.03) rectangle (421.57,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,103.03) --
	( 60.61,105.88) --
	( 64.85,107.46) --
	( 64.98,107.51) --
	( 78.30,112.49) --
	( 86.71,115.63) --
	( 92.34,117.73) --
	( 95.59,118.94) --
	(101.92,121.31) --
	(110.88,124.66) --
	(154.64,141.01) --
	(158.01,142.26) --
	(171.43,147.28) --
	(178.49,149.91) --
	(187.92,153.44) --
	(192.71,155.23) --
	(195.62,156.31) --
	(195.71,156.34) --
	(196.35,156.58) --
	(198.04,157.22) --
	(199.87,157.90) --
	(204.99,159.81) --
	(205.19,159.89) --
	(209.65,161.55) --
	(211.50,162.24) --
	(215.87,163.88) --
	(217.33,164.42) --
	(217.43,164.46) --
	(217.68,164.55) --
	(218.17,164.74) --
	(220.17,165.48) --
	(220.33,165.54) --
	(220.93,165.77) --
	(221.63,166.03) --
	(222.58,166.39) --
	(223.29,166.65) --
	(223.54,166.74) --
	(223.59,166.76) --
	(224.00,166.92) --
	(229.14,168.84) --
	(231.15,169.59) --
	(231.34,169.66) --
	(232.39,170.05) --
	(233.34,170.41) --
	(234.24,170.74) --
	(235.24,171.11) --
	(236.22,171.48) --
	(237.40,171.92) --
	(237.41,171.93) --
	(239.29,172.63) --
	(239.31,172.63) --
	(240.03,172.90) --
	(240.80,173.19) --
	(241.27,173.36) --
	(241.65,173.51) --
	(242.95,173.99) --
	(244.78,174.68) --
	(248.30,175.99) --
	(249.74,176.53) --
	(250.22,176.71) --
	(250.38,176.77) --
	(250.69,176.88) --
	(251.97,177.36) --
	(252.46,177.55) --
	(253.69,178.00) --
	(253.89,178.08) --
	(254.34,178.25) --
	(255.73,178.77) --
	(256.94,179.22) --
	(258.99,179.99) --
	(260.08,180.39) --
	(260.16,180.42) --
	(261.39,180.88) --
	(262.57,181.32) --
	(263.47,181.66) --
	(264.14,181.91) --
	(264.43,182.02) --
	(264.94,182.21) --
	(265.11,182.27) --
	(265.48,182.41) --
	(265.54,182.43) --
	(266.69,182.86) --
	(266.70,182.87) --
	(267.74,183.26) --
	(267.83,183.29) --
	(267.95,183.33) --
	(268.15,183.41) --
	(268.32,183.47) --
	(268.51,183.54) --
	(268.75,183.63) --
	(269.12,183.77) --
	(269.30,183.84) --
	(269.75,184.01) --
	(269.91,184.06) --
	(271.51,184.66) --
	(272.31,184.96) --
	(272.40,184.99) --
	(272.91,185.18) --
	(273.01,185.22) --
	(273.29,185.33) --
	(273.48,185.40) --
	(274.31,185.71) --
	(274.85,185.91) --
	(274.88,185.92) --
	(275.50,186.15) --
	(276.03,186.35) --
	(276.14,186.39) --
	(276.73,186.61) --
	(276.77,186.63) --
	(277.28,186.82) --
	(277.37,186.85) --
	(278.83,187.40) --
	(278.93,187.44) --
	(278.99,187.46) --
	(279.03,187.47) --
	(279.36,187.60) --
	(279.83,187.77) --
	(279.90,187.80) --
	(280.21,187.91) --
	(280.36,187.97) --
	(280.41,187.99) --
	(280.47,188.01) --
	(280.50,188.02) --
	(280.60,188.06) --
	(280.63,188.07) --
	(281.16,188.27) --
	(281.52,188.40) --
	(281.60,188.43) --
	(283.10,188.99) --
	(283.28,189.06) --
	(283.34,189.08) --
	(283.74,189.23) --
	(283.80,189.25) --
	(284.26,189.42) --
	(284.43,189.49) --
	(284.75,189.61) --
	(284.80,189.63) --
	(284.81,189.63) --
	(284.81,189.63) --
	(284.84,189.64) --
	(284.88,189.66) --
	(285.44,189.87) --
	(285.67,189.95) --
	(286.04,190.09) --
	(286.70,190.34) --
	(286.95,190.43) --
	(287.76,190.74) --
	(288.16,190.88) --
	(288.45,190.99) --
	(288.86,191.14) --
	(289.03,191.21) --
	(289.13,191.24) --
	(289.30,191.31) --
	(289.61,191.42) --
	(289.71,191.46) --
	(289.99,191.56) --
	(290.44,191.73) --
	(291.29,192.05) --
	(291.45,192.11) --
	(291.58,192.16) --
	(292.20,192.39) --
	(292.36,192.45) --
	(292.77,192.60) --
	(292.78,192.61) --
	(292.85,192.64) --
	(292.94,192.67) --
	(293.49,192.88) --
	(293.61,192.92) --
	(293.90,193.03) --
	(293.94,193.04) --
	(295.12,193.48) --
	(295.85,193.76) --
	(296.61,194.04) --
	(297.11,194.23) --
	(297.99,194.55) --
	(298.09,194.59) --
	(298.13,194.61) --
	(298.21,194.64) --
	(298.45,194.73) --
	(298.48,194.74) --
	(298.71,194.82) --
	(298.89,194.89) --
	(299.22,195.01) --
	(300.07,195.33) --
	(300.69,195.56) --
	(301.34,195.81) --
	(301.81,195.98) --
	(301.86,196.00) --
	(302.06,196.07) --
	(302.08,196.08) --
	(302.20,196.13) --
	(302.30,196.16) --
	(302.45,196.22) --
	(302.52,196.25) --
	(302.61,196.28) --
	(302.89,196.39) --
	(302.93,196.40) --
	(303.17,196.49) --
	(304.10,196.84) --
	(304.31,196.92) --
	(304.47,196.98) --
	(304.48,196.98) --
	(304.60,197.02) --
	(304.68,197.06) --
	(305.11,197.22) --
	(305.28,197.28) --
	(305.76,197.46) --
	(305.86,197.49) --
	(306.15,197.60) --
	(307.03,197.93) --
	(307.16,197.98) --
	(307.37,198.06) --
	(308.42,198.45) --
	(308.63,198.53) --
	(308.79,198.59) --
	(309.08,198.70) --
	(309.55,198.87) --
	(309.72,198.94) --
	(310.36,199.18) --
	(310.45,199.21) --
	(310.80,199.34) --
	(310.98,199.41) --
	(311.09,199.45) --
	(311.49,199.60) --
	(311.71,199.68) --
	(311.87,199.74) --
	(312.39,199.93) --
	(312.68,200.04) --
	(312.75,200.07) --
	(314.09,200.57) --
	(314.12,200.58) --
	(314.55,200.74) --
	(314.84,200.85) --
	(315.05,200.93) --
	(315.28,201.01) --
	(315.54,201.11) --
	(315.61,201.14) --
	(315.65,201.15) --
	(316.29,201.39) --
	(316.37,201.42) --
	(316.58,201.50) --
	(316.61,201.51) --
	(316.72,201.55) --
	(317.13,201.71) --
	(318.60,202.25) --
	(319.14,202.45) --
	(320.71,203.04) --
	(321.34,203.28) --
	(321.47,203.33) --
	(322.56,203.73) --
	(322.64,203.76) --
	(322.93,203.87) --
	(323.98,204.26) --
	(324.06,204.29) --
	(324.53,204.47) --
	(324.82,204.58) --
	(325.46,204.82) --
	(325.85,204.96) --
	(325.87,204.97) --
	(325.91,204.99) --
	(326.16,205.08) --
	(326.46,205.19) --
	(327.01,205.40) --
	(327.50,205.58) --
	(327.78,205.68) --
	(328.37,205.91) --
	(328.92,206.11) --
	(330.17,206.58) --
	(330.38,206.66) --
	(330.88,206.84) --
	(333.53,207.83) --
	(333.56,207.84) --
	(333.69,207.89) --
	(333.82,207.94) --
	(333.83,207.94) --
	(335.38,208.52) --
	(335.47,208.56) --
	(337.65,209.37) --
	(338.50,209.69) --
	(338.83,209.81) --
	(338.87,209.83) --
	(339.04,209.89) --
	(339.21,209.95) --
	(339.40,210.03) --
	(339.55,210.08) --
	(339.76,210.16) --
	(339.84,210.19) --
	(340.15,210.31) --
	(340.28,210.35) --
	(340.65,210.49) --
	(341.52,210.82) --
	(342.53,211.20) --
	(343.79,211.66) --
	(343.95,211.72) --
	(345.11,212.16) --
	(345.20,212.19) --
	(345.78,212.41) --
	(346.49,212.67) --
	(346.80,212.79) --
	(346.94,212.84) --
	(347.30,212.98) --
	(348.63,213.47) --
	(348.84,213.55) --
	(349.59,213.83) --
	(350.01,213.99) --
	(350.27,214.09) --
	(350.57,214.20) --
	(351.61,214.59) --
	(352.50,214.92) --
	(354.60,215.70) --
	(354.77,215.77) --
	(355.03,215.86) --
	(355.06,215.88) --
	(355.38,215.99) --
	(355.44,216.02) --
	(355.66,216.10) --
	(355.69,216.11) --
	(356.06,216.25) --
	(356.08,216.25) --
	(356.57,216.44) --
	(356.86,216.55) --
	(356.99,216.60) --
	(357.04,216.61) --
	(357.10,216.64) --
	(357.28,216.70) --
	(357.68,216.85) --
	(357.71,216.86) --
	(358.36,217.11) --
	(358.45,217.14) --
	(358.80,217.27) --
	(359.58,217.56) --
	(360.14,217.77) --
	(360.17,217.78) --
	(360.28,217.83) --
	(360.68,217.98) --
	(362.54,218.67) --
	(362.92,218.81) --
	(362.99,218.84) --
	(362.99,218.84) --
	(363.68,219.09) --
	(363.71,219.11) --
	(364.25,219.31) --
	(364.57,219.43) --
	(364.77,219.50) --
	(365.00,219.59) --
	(365.26,219.68) --
	(365.84,219.90) --
	(365.84,219.90) --
	(365.92,219.93) --
	(366.04,219.98) --
	(366.47,220.14) --
	(367.05,220.35) --
	(368.20,220.78) --
	(368.39,220.85) --
	(368.50,220.90) --
	(370.21,221.53) --
	(371.17,221.89) --
	(371.58,222.05) --
	(372.02,222.21) --
	(373.58,222.79) --
	(376.96,224.06) --
	(378.52,224.64) --
	(383.85,226.63) --
	(384.44,226.85) --
	(384.92,227.03) --
	(385.30,227.17) --
	(385.73,227.33) --
	(385.96,227.42) --
	(386.70,227.69) --
	(386.81,227.74) --
	(387.17,227.87) --
	(387.19,227.88) --
	(387.24,227.89) --
	(387.39,227.95) --
	(387.67,228.06) --
	(388.26,228.28) --
	(389.16,228.61) --
	(389.82,228.86) --
	(390.40,229.08) --
	(390.44,229.09) --
	(390.79,229.22) --
	(391.07,229.32) --
	(395.16,230.85) --
	(396.00,231.17) --
	(396.15,231.23) --
	(403.52,233.98) --
	(404.02,234.17);

@@

\path[fill=fillColor,fill opacity=0.30] ( 52.97,162.09) --
	( 60.61,163.40) --
	( 64.85,164.12) --
	( 64.98,164.14) --
	( 78.30,166.42) --
	( 86.71,168.04) --
	( 92.34,169.01) --
	( 95.59,169.59) --
	(101.92,170.70) --
	(110.88,172.06) --
	(154.64,179.67) --
	(158.01,180.30) --
	(171.43,182.97) --
	(178.49,184.48) --
	(187.92,186.36) --
	(192.71,187.31) --
	(195.62,187.86) --
	(195.71,187.88) --
	(196.35,187.99) --
	(198.04,188.42) --
	(199.87,188.91) --
	(204.99,189.74) --
	(205.19,189.76) --
	(209.65,190.87) --
	(211.50,191.30) --
	(215.87,192.29) --
	(217.33,192.57) --
	(217.43,192.60) --
	(217.68,192.66) --
	(218.17,192.79) --
	(220.17,193.36) --
	(220.33,193.40) --
	(220.93,193.57) --
	(221.63,193.74) --
	(222.58,193.90) --
	(223.29,194.07) --
	(223.54,194.12) --
	(223.59,194.12) --
	(224.00,194.20) --
	(229.14,195.35) --
	(231.15,195.91) --
	(231.34,195.96) --
	(232.39,196.26) --
	(233.34,196.54) --
	(234.24,196.77) --
	(235.24,197.03) --
	(236.22,197.29) --
	(237.40,197.62) --
	(237.41,197.63) --
	(239.29,198.08) --
	(239.31,198.09) --
	(240.03,198.24) --
	(240.80,198.41) --
	(241.27,198.49) --
	(241.65,198.60) --
	(242.95,198.93) --
	(244.78,199.36) --
	(248.30,200.44) --
	(249.74,200.85) --
	(250.22,200.95) --
	(250.38,200.98) --
	(250.69,201.04) --
	(251.97,201.34) --
	(252.46,201.45) --
	(253.69,201.74) --
	(253.89,201.77) --
	(254.34,201.93) --
	(255.73,202.30) --
	(256.94,202.63) --
	(258.99,203.26) --
	(260.08,203.53) --
	(260.16,203.56) --
	(261.39,203.93) --
	(262.57,204.32) --
	(263.47,204.60) --
	(264.14,204.79) --
	(264.43,204.83) --
	(264.94,204.99) --
	(265.11,205.04) --
	(265.48,205.19) --
	(265.54,205.22) --
	(266.69,205.53) --
	(266.70,205.53) --
	(267.74,205.91) --
	(267.83,205.95) --
	(267.95,205.98) --
	(268.15,206.06) --
	(268.32,206.13) --
	(268.51,206.20) --
	(268.75,206.30) --
	(269.12,206.38) --
	(269.30,206.42) --
	(269.75,206.58) --
	(269.91,206.63) --
	(271.51,207.18) --
	(272.31,207.50) --
	(272.40,207.51) --
	(272.91,207.57) --
	(273.01,207.60) --
	(273.29,207.71) --
	(273.48,207.75) --
	(274.31,208.12) --
	(274.85,208.26) --
	(274.88,208.27) --
	(275.50,208.41) --
	(276.03,208.59) --
	(276.14,208.64) --
	(276.73,208.88) --
	(276.77,208.90) --
	(277.28,209.09) --
	(277.37,209.13) --
	(278.83,209.65) --
	(278.93,209.68) --
	(278.99,209.70) --
	(279.03,209.72) --
	(279.36,209.80) --
	(279.83,209.97) --
	(279.90,209.99) --
	(280.21,210.08) --
	(280.36,210.11) --
	(280.41,210.13) --
	(280.47,210.14) --
	(280.50,210.15) --
	(280.60,210.19) --
	(280.63,210.21) --
	(281.16,210.43) --
	(281.52,210.53) --
	(281.60,210.56) --
	(283.10,211.02) --
	(283.28,211.07) --
	(283.34,211.08) --
	(283.74,211.19) --
	(283.80,211.20) --
	(284.26,211.35) --
	(284.43,211.41) --
	(284.75,211.52) --
	(284.80,211.53) --
	(284.81,211.53) --
	(284.81,211.53) --
	(284.84,211.54) --
	(284.88,211.55) --
	(285.44,211.71) --
	(285.67,211.78) --
	(286.04,211.92) --
	(286.70,212.18) --
	(286.95,212.27) --
	(287.76,212.58) --
	(288.16,212.69) --
	(288.45,212.78) --
	(288.86,212.95) --
	(289.03,213.03) --
	(289.13,213.07) --
	(289.30,213.15) --
	(289.61,213.29) --
	(289.71,213.33) --
	(289.99,213.42) --
	(290.44,213.59) --
	(291.29,213.88) --
	(291.45,213.94) --
	(291.58,213.99) --
	(292.20,214.21) --
	(292.36,214.25) --
	(292.77,214.40) --
	(292.78,214.41) --
	(292.85,214.44) --
	(292.94,214.46) --
	(293.49,214.61) --
	(293.61,214.65) --
	(293.90,214.73) --
	(293.94,214.74) --
	(295.12,215.14) --
	(295.85,215.49) --
	(296.61,215.80) --
	(297.11,216.00) --
	(297.99,216.38) --
	(298.09,216.43) --
	(298.13,216.45) --
	(298.21,216.47) --
	(298.45,216.56) --
	(298.48,216.57) --
	(298.71,216.64) --
	(298.89,216.70) --
	(299.22,216.84) --
	(300.07,217.14) --
	(300.69,217.37) --
	(301.34,217.66) --
	(301.81,217.84) --
	(301.86,217.86) --
	(302.06,217.94) --
	(302.08,217.95) --
	(302.20,218.00) --
	(302.30,218.03) --
	(302.45,218.06) --
	(302.52,218.09) --
	(302.61,218.13) --
	(302.89,218.23) --
	(302.93,218.25) --
	(303.17,218.34) --
	(304.10,218.73) --
	(304.31,218.82) --
